LwM2M TITLE WIP

### 2024-10-16 paper.tex
pre-review version

\author{Jaime Jiménez}
\email{jaime.jimenez@ericsson.com}
\orcid{0009-0008-2864-4269}
\affiliation{%
  \institution{Ericsson}
  \city{Jorvas}
  \country{Finland}
}
\author{Matthew Gillmore}
\email{email@email}
\orcid{orcidID}
\affiliation{%
  \institution{Itron}
  \city{City}
  \country{Country}
}

\begin{abstract}
%Jaime: Write a concise abstract (150-250 words) summarizing the paper's purpose, methods, key findings, and implications.
TBD.

@@

\keywords{IoT, network management, LwM2M, device management, protocol, scalability, security}

@@

The IAB "NEMOPS" workshop seeks contributions that critically assess the progress made since the 2002 IAB workshop, particularly in terms of network management protocols. This paper aims to present LwM2M's as a new protocol created in 2017 that addresses the needs for managing IoT endpoints from the operational point of view of device and network management.

@@

The LwM2M data model enables servers to access individual resources, instances, or entire objects using well-defined URI strings. The format of these URIs is as follows:

@@

All objects are listed in the LwM2M Registry~\cite{lwm2m-registry}, categorized as either application-oriented (e.g., thermostats, lamps) or system-oriented (e.g., security, connectivity).

@@

LwM2M, though robust in its core functionalities, has advanced significantly through various extensions and integrations. This section explores recent research developments that may inspire its future evolution.
%Jaime: Expand on the implications of these integrations for the future of IoT and network management.

LwM2M has become a central focus in IoT research due to its improved security, in particular for firmware updates ~\cite{8725488} and integration with other technologies.

@@

\section{LwM2M Operations} \label{operations}
%Jaime: Develop this section to cover typical operations, challenges, and best practices. Include examples of common operations and how they're implemented.
%Jaime: Add more specific examples of how LwM2M is used in real-world applications.

TBD

@@

TBD

@@

We'd like to thank XYZ for their support of this work. We also appreciate A, B, C for their valuable discussions on this topic.

>>>>

\author{Jaime Jiménez}
\email{jaime.jimenez@ericsson.com}
\orcid{0009-0008-2864-4269}
\affiliation{%
  \institution{Ericsson}
  \city{Jorvas}
  \country{Finland}
}

\begin{abstract}

This paper provides an overview of the Lightweight Machine-to-Machine (LwM2M) protocol, highlighting its role in IoT device management and its integration with key IETF standards such as CoAP, DTLS, and OSCORE. While network management protocols like SNMP, RESTCONF, and CORECONF focus on monitoring and configuring endpoints within the network, LwM2M extends these capabilities by managing the entire lifecycle of individual devices, including configuration, control, and maintenance. We discuss LwM2M's architecture, data model, communication interfaces, and explore recent advancements in the protocol.

@@

\keywords{Internet of Things, IoT, network management, device management, security, standards}

@@

The IAB "NEMOPS" workshop seeks contributions that critically assess the progress made since the 2002 IAB workshop, particularly in terms of network management protocols. This paper aims to present LwM2M, an management protocol that addresses the needs for managing IoT endpoints from the operational point of view of device and network management.

@@

The LwM2M data model enables servers to access individual resources, instances, or entire objects using well-defined URI strings. The URI template approach follows the Web Linking and the IETF CoRE Link Format~\cite{rfc6690}. The format is as follows:

@@

All objects are listed in the LwM2M Registry~\cite{lwm2m-registry}, categorized as either application-oriented (e.g., thermostats, lamps) or system-oriented (e.g., security, connectivity). Those for applications follow the same schema and come from the IP for Smart Objects (IPSO)~\cite{ipso} consortium which was integrated into OMA.

Semantically, the object type represents a single measurement, actuation, or control point for example a temperature sensor, a light (actuator), or an on-off switch (control point). A resource specifies a particular view or active property of an object. For example, a temperature sensor object might expose the current value (most recent reading), also the minimum and maximum possible reading, the minimum and maximum reading in an interval, and attributes like engineering units and application type. Attributes describe the metadata configuration, settings, and state of an object or resource, and are discoverable by reading the link-format data of an object or resource. Multiple attributes may be serialized in the link-format descriptors that an object exposes.

@@

LwM2M, though robust in its core functionalities, has advanced significantly through various extensions and integrations. This section explores recent research developments that may inspire its future evolution. LwM2M has become a central focus in IoT research due to its improved security, in particular for firmware updates ~\cite{8725488} and integration with other technologies.

@@

@@

In this paper, we have presented an overview of LwM2M and its components, the dependencies on IETF standards and some potential new building blocks for future additions.

@@

We'd like to thank Ericsson for their support of this work.
